### 2017-07-08 paper/conclu.tex
OK

\noindent{\em Non-probabilistic programs.}
Termination analysis of non-probabilistic programs has also been extensively 
studied~\cite{PR04:transition-invariants, 
CPR06:terminator,DBLP:conf/cav/BradleyMS05,DBLP:conf/tacas/ColonS01, 
DBLP:conf/vmcai/PodelskiR04,DBLP:conf/pods/SohnG91,BMS05b,LJB01,KSTW10:compositional-transition-invariants,
 CPR11:termination-cacm}.
Ranking functions are at the heart of the termination analysis, and lexicographic 
ranking function has emerged as one of the most efficient and practical approaches
for termination 
analysis~\cite{DBLP:conf/cav/BradleyMS05,CSZ13,ADFG10:lexicographic,GMR15:rank-extremal},

being used e.g. in 
the prominent \texttt{T2} temporal prover~\cite{BCIKP16:T2}.
In this work we extend lexicographic ranking functions to probabilistic 
programs,
and present lexicographic RSMs for almost-sure termination analysis of probabilistic programs
with non-determinism. Theoretical complexity of synthesizing lexicographic 
ranking functions in non-probabilistic programs was studied 
in~\cite{BG13:integer-ranking,BG15:lexicographic-complexity}.

>>>>

\noindent{\em Non-probabilistic programs.}
Termination analysis of non-probabilistic programs has also been extensively 
studied~\cite{PR04:transition-invariants, 
CPR06:terminator,DBLP:conf/cav/BradleyMS05,DBLP:conf/tacas/ColonS01, 
DBLP:conf/vmcai/PodelskiR04,DBLP:conf/pods/SohnG91,BMS05b,LJB01,KSTW10:compositional-transition-invariants,
 CPR11:termination-cacm}.
Ranking functions are at the heart of the termination analysis, and lexicographic 
ranking function has emerged as one of the most efficient and practical approaches
for termination 
analysis~\cite{DBLP:conf/cav/BradleyMS05,CSZ13,ADFG10:lexicographic,GMR15:rank-extremal},
being used e.g. in 
the prominent \texttt{T2} temporal prover~\cite{BCIKP16:T2}.
In this work we extend lexicographic ranking functions to probabilistic 
programs,
and present lexicographic RSMs for almost-sure termination analysis of probabilistic programs
with non-determinism. Theoretical complexity of synthesizing lexicographic 
ranking functions in non-probabilistic programs was studied 
in~\cite{BG13:integer-ranking,BG15:lexicographic-complexity}.
